Regular singular Volterra equations on complex domains

### 2023-08-31 reg-sing-volterra.tex
Work on Laplace transform section

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It's a function on the frequency domain because it depends on the frequency variable $z$.
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

Fractional integration has a smoothing effect: it reduces the sharpness of any power-law singularity at $\zeta = \alpha$.
\begin{prop}\label{prop:frac-int-smoothing}
For each $\nu \in (0, \infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ maps
\[ \varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
continuously for all $\sigma > -1$ and $\Lambda \ge 0$.
\end{prop}
\begin{proof}
Rewrite the fractional integral as
\begin{align*}
\left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \; d\zeta\\
&=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,\varphi \; d\zeta.
\end{align*}
The Volterra operator with kernel
\[ h(a, a') = \frac{1}{\Gamma(\nu)}\,\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a)- \alpha} \]
satisfies Condition~\eqref{cond:eps-lambda} with $\gamma=\nu-1$ and $\lambda_\Delta=0$, as long as we loosen the condition to allow any $\gamma > -1$. Hence, by Proposition~\ref{prop:smoothing}, this operator maps
\[ \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
continuously for all $\sigma > -1$ and $\Lambda \ge 0$. Multiplication by $\zeta - \alpha$ then maps
\[ \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
continuously.
\end{proof}

From Proposition \ref{prop:frac-int-smoothing}, we deduce that $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ has a well-defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$. Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that 
\[ \laplace_{\zeta,\alpha}^{\theta}\,\fracderiv{-\nu}{\zeta}{\alpha} \varphi = z^{-\nu} \laplace_{\zeta, \alpha}^{\theta} \varphi \]
for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$. This generalizes the Laplace transform's action on derivatives: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
for all integers $n \ge 0$ and suitable directions $\theta$.

>>>>

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$,
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It's a function on the frequency domain because it depends on the frequency variable $z$.
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\mu}{\zeta}{\alpha}\,\fracderiv{-\nu}{\zeta}{\alpha} & = \fracderiv{-\mu-\nu}{\zeta}{\alpha} & \mu, \nu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

Fractional integration has a smoothing effect: it reduces the sharpness of any power-law singularity at $\zeta = \alpha$.
\begin{prop}\label{prop:frac-int-smoothing}
For each $\nu \in (0, \infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ maps
\[ \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
continuously for all $\sigma > -1$ and $\Lambda \ge 0$.
\end{prop}
\begin{proof}
Rewrite the fractional integral as
\begin{align*}
\left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \; d\zeta\\
&=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,\varphi \; d\zeta.
\end{align*}
The Volterra operator with kernel
\[ h(a, a') = \frac{1}{\Gamma(\nu)}\,\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a)- \alpha} \]
satisfies Condition~\eqref{cond:eps-lambda} with $\gamma=\nu-1$ and $\lambda_\Delta=0$, as long as we loosen the condition to allow any $\gamma > -1$. Hence, by Proposition~\ref{prop:smoothing}, this operator maps
\[ \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
continuously for all $\sigma > -1$ and $\Lambda \ge 0$. Multiplication by $\zeta - \alpha$ then maps
\[ \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
continuously.
\end{proof}

From Proposition~\ref{prop:frac-int-smoothing}, we deduce that when $\varphi$ belongs to $\singexpalg{\sigma}(\domain_\alpha)$ for some $\sigma > -1$, its fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ has a well-defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$. Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that 
\[ \laplace_{\zeta,\alpha}^{\theta}\,\fracderiv{-\nu}{\zeta}{\alpha} \varphi = z^{-\nu} \laplace_{\zeta, \alpha}^{\theta} \varphi \]
for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$. This generalizes the Laplace transform's action on derivatives: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
for all integers $n \ge 0$ and suitable directions $\theta$.
